Posterior comparison methods

### 2022-11-01 src/explore_posterior-comparison/posterior-comparison.Rmd
Trying to add model1_icar_index, and setting up dev-sinla to work well with this

```{r}
samples <- readRDS("depends/samples-m250.rds")
samples_mcmc <- samples$mcmc
samples_gaussian <- samples$gaussian
samples_laplace <- samples$laplace
```

>>>>

```{r}
samples <- readRDS("depends/model1-samples-m250.rds")
samples_mcmc <- samples$mcmc
samples_gaussian <- samples$gaussian
samples_laplace <- samples$laplace
```
